Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
Kcmb to MJy/sr conversion equation

This equation is quite similar to Equation \ref{equ:broadband}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the broadband intensity 
measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for
all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr.

@@

To reiterate, $u_{\nu_i}(T_k, \beta_k)$ has units of (MJy/sr)/$K_{CMB}$, and
therefore $I_{\nu_{i}}$ will have different units depending on the band 
$\nu_i$, though $I_{\nu_{i}}$ always has the same units as the native 
\PLANCK~HFI band $\nu_i$ map.

>>>>

This equation is quite similar to Equation \ref{equ:broadband}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the broadband intensity 
measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 (dimensionless) for
all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr:

@@

\begin{equation}
u_{\nu_i}(T, \beta) = u_{\nu_i, IRAS} \times u_{\nu_i, IRAS \ to \ (T, \beta)}
\end{equation}

Here $u_{\nu_i, IRAS}$ gives the conversion factor from $K_{CMB}$ to MJy/sr
for band $\nu_i$ under the `\IRAS~convention', which corresponds to
a spectral index $\alpha$=$-1$ spectrum. The values of $u_{\nu_i, IRAS}$
are listed in the second column of \cite{planckresponse} Table 6. 
$u_{\nu_i, IRAS \ to \ (T, \beta)}$ is a color correction factor relative to
the \IRAS~convention for band $\nu_i$ and a MBB($T$, $\beta$) spectrum.
To reiterate, for $\nu_i$$\le$353 GHz $u_{\nu_i}(T_k, \beta_k)$ has units 
of (MJy/sr)/$K_{CMB}$, and therefore $I_{\nu_{i}}$ will have different 
units depending on the band $\nu_i$, though $I_{\nu_{i}}$ always has 
the same units as the native band $\nu_i$ map.
